Replicate earlier study

### 2023-04-02 x_replicate.qmd
moving towards spacing deviation

```{r}
tessel_info <- make_tessel_db_entry(mickey |> filter(ARR, !ORPHAN))
tessel_info
```

@@

>>>>

```{r}
tessel_info <- make_tessel_db_entry(mickey |> filter(ARR, !ORPHAN))

tessel_info
```

@@

```{r}
if(file.exists(tessel_fn)) { message("Open existing tessel database")
}else{
  message("Create tessel database")
    tessel_info |> 
    dplyr::select(H3_BIN, RWY, TIME_2GO, DIST_2GO, UID ) |> 
    dplyr::ungroup() |> 
    readr::write_csv(tessel_fn)
  }
```

t-digest (for paper to DASC?)
https://git.sr.ht/~hrbrmstr/tdigest

```{r}
tessel_lookup <- readr::read_csv(tessel_fn, show_col_types = FALSE) |> 
  group_by(H3_BIN, RWY) |> 
  summarise( TIME_MIN = min(TIME_2GO), TIME_Q5 = quantile(TIME_2GO, probs = 0.05)
            , DIST_MIN= min(DIST_2GO), DIST_Q5 = quantile(DIST_2GO, probs = 0.05)
            , SAMPLE_N = n())
```

```{r}
tmp <- mickey |> filter(UID %in% study_sequences$UID[1:4]) |> 
  select(UID, RWY2 = RWY, ALDT, study_trj) |> 
  unnest(study_trj)

ggplot(data = tmp) +
  geom_point(aes(x = TIME, y = ALT_B))
```

spacing deviation (t) = min time (trailer (t)) –    min time (leader (t – s))

```{r}
add_bin_mins <- function(.trj, .bins){
  trj <- .trj %>%
    left_join(.bins %>% select(H3_BIN, RWY, MIN_DIST_2GO, MIN_TIME_2GO)
              , by = c("RWY", "H3_BIN"))
  return(trj)
}

calc_pairwise_spacing <- function(.uid, .seq_uid, .t_trail , .ds, .bins = bins){

  leader <- .ds %>% filter(UID == .uid) %>% 
    add_bin_mins(.bins) %>%
    select(UID, TIME, RWY, DIST_2GO, TIME_2GO, MIN_DIST_2GO, MIN_TIME_2GO)

  trailer<- .ds %>% filter(UID == .seq_uid) %>% 
    add_bin_mins(.bins) %>%
    select(UID, TIME, RWY, DIST_2GO, TIME_2GO, MIN_DIST_2GO, MIN_TIME_2GO) %>% 
    mutate(TIME_WARP = TIME - .t_trail)  %>%
    rename(SEQ_UID = UID, SEQ_DIST_2GO = DIST_2GO, SEQ_TIME_2GO = TIME_2GO
          ,SEQ_MIN_DIST_2GO = MIN_DIST_2GO, SEQ_MIN_TIME_2GO = MIN_TIME_2GO)

  spacedev <- leader %>% 
    left_join(trailer, by = c("TIME" = "TIME_WARP", "RWY")) %>% 
    mutate(MIN_TIME_OFF = MIN_TIME_2GO - SEQ_MIN_TIME_2GO
         , MIN_DIST_OFF = MIN_DIST_2GO - SEQ_MIN_DIST_2GO
         , DIST_OFF     = DIST_2GO - SEQ_DIST_2GO
         , STEP = row_number()) %>% 
    select(UID, SEQ_UID, STEP, MIN_TIME_OFF, MIN_DIST_OFF, DIST_OFF, everything())

return(spacedev)
}

#' Smoothing function 
#' wrapper for slider::slide()

roll_median <- function(.df, .var, .whs, .target_var){
  df <- .df %>% 
    mutate(
     {{.target_var}} := slider::slide_dbl({{.var}}, median, .before = .whs, .after = .whs)
  )
}

```
